\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-29 paper/ms.tex
Add JMB affiliation

\author{
  Semyeong Oh$^{1,*}$,\,
  Adrian M. Price-Whelan$^{1}$,\,
  John M. Brewer$^{2}$,\,\\
  David W. Hogg$^{3,4,5,6}$,\,
  David N. Spergel$^{1,3}$,\,
  Justin Myles$^{2}$
}
\date{\small\today}

@@

% affiliations
\vspace{-1cm}
{\small\noindent
  $^1$Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA \\
  $^2$Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA \\
  $^3$Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA \\
  $^4$Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA \\
  $^5$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA \\
  $^6$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg \\
  $^*$To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}
}

>>>>

\author{
  Semyeong Oh$^{1,*}$,\,
  Adrian M. Price-Whelan$^{1}$,\,
  John M. Brewer$^{2,3}$,\,\\
  David W. Hogg$^{4,5,6,7}$,\,
  David N. Spergel$^{1,4}$,\,
  Justin Myles$^{2}$
}
\date{\small\today}

@@

% affiliations
\vspace{-1cm}
{\small\noindent
  $^1$Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA \\
  $^2$Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA \\
  $^3$Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA \\
  $^4$Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA \\
  $^5$Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA \\
  $^6$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA \\
  $^7$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg \\
  $^*$To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}
}
